TGI-spinal-power

### 2022-06-23 analysis/tgispine_zoib_power-sim.Rmd

# Plotting data distributions to see what kind of model family is required
df50$quality <- factor(df50$quality, 
                             levels = c("cold", "warm", "burn"))
ggplot2::ggplot(data = df50) +
  geom_histogram(aes(rating, fill = stimuli), alpha = .5, binwidth = .05) +
  facet_wrap(~quality) +
  theme_classic()
```

@@

## SIMULATIONS ##
# Run through n = 1000 simulations of the pilot data, and extract p-value for the smallest effect (cold_location) of each model
# Extract the power from each model - first cold
```{r}
# the warm model has the smallest effect size, so should extract power calculation for both the cold and warm only
# do this for 40 participants, for 1000 simulations
nSims <- 1000
n <- 32 # number of participants to simulate
po_c <- data.frame()
po_w <- data.frame()
for (i in 1:nSims){
  # creating individual data-frames from simulated data
  df_sim <- data.frame()
  for (i in 1:n) {
    df <- simulate_subj(i)
    # simulating proportion of zero responses into the data using prop_zero (defined above)
    # this is a bit raw, but works!
    df_c <- prop_zero(df, 'cold')
    df_w <- prop_zero(df, 'warm')
    df_b <- prop_zero(df, 'burn')
    # bind all
    df_z <- rbind(df_c, df_w)
    df_z <- rbind(df_z, df_b)

>>>>

# Plotting data distributions to see what kind of model family is required
df50$quality <- factor(df50$quality, 
                             levels = c("cold", "warm", "burn"))
ggplot2::ggplot(data = df50) +
  geom_histogram(aes(rating, fill = stimuli), alpha = .5, binwidth = .05, position = "identity") +
  facet_wrap(~quality) +
  theme_classic()
```

@@

## SIMULATIONS
# Run through n = 1000 simulations of the pilot data, and extract p-value for the smallest effect (cold_location) of each model
# Extract the power from each model - first cold
```{r}
# the warm model has the smallest effect size, so should extract power calculation for both the cold and warm only
# do this for 40 participants, for 1000 simulations
nSims <- 1000
n <- 32 # number of participants to simulate
po_c <- data.frame()
po_w <- data.frame()
for (i in 1:nSims){
  # creating individual data-frames from simulated data
  df_sim <- data.frame()
  for (i in 1:n) {
    df <- simulate_subj(i)
    # simulating proportion of zero responses into the data using prop_zero (defined above)
    # this is a bit raw, but works!
    df_c <- prop_zero(df, 'cold')
    df_w <- prop_zero(df, 'warm')
    df_b <- prop_zero(df, 'burn')
    # bind all
    df_z <- rbind(df_c, df_w)
    df_z <- rbind(df_z, df_b)
